\section*{Abstract}
	In this thesis, the KIT-Motion-Language dataset\cite{Plappert2016} will be used to evaluate learning machines for the purpose of human activity recognition. Some networks, such as Recurrent Neural Networks, can model temporal dependencies in sequences, and therefore provide a solid theoretical basis for time-series classification task. Nevertheless, vanilla learning machines that build a one-to-one relationship between the data and the labels can perform better than recurrent neural networks, which are specially devised for sequence modeling. This thesis will investigate these assumptions using a suite of vanilla and sequence modeling neural networks by gauging their performance in a comparative study. To facilitate that, a small framework was built to experiment with and evaluate these learning machines.
\section*{Zusammenfassung}
	In dieser Arbeit wird der KIT-Motion-Language Datensatz\cite{Plappert2016} verwendet, um maschinelles Lernen Algorithmen für den Zweck der menschlichen Aktivitätserkennung zu evaluieren. Wobei einige Modelle Sequenzen besser modellieren als andere und eine bessere theoretische Grundlage bieten, warum das der Fall ist. Learning Machines, die eine Eins-zu-Eins-Beziehung zwischen den Daten und den Labels bilden, können besser leisten als rekurrente neuronale Netze, die speziell für die Sequenzmodellierung modelliert sind. In dieser Arbeit wird dies anhand einer Reihe von tief- und \newline Sequenzmodellierungs-Neuronalnetzen untersucht und ihre Leistung in einer vergleichenden Studie bewertet. Um dies zu erleichtern, wurde ein kleines Framework erstellt, mit dem die Daten aus dem KIT Bewegungsdatensatz extrahiert und die Leaning Machines getestet und bewertet werden können. 
